---
title: "FinalProject631-02"
author: "Andy Xiong"
date: "5/11/2022"
output: pdf_document
---

We are going to look at multiple NFL Passing Data set from the year 2010-2018. They are all separate data sets so we can look into an individual year. 
I want to see if we see the trend for passing yards go up over time and see if their were any specific person responsible. 
I also wanted to try and combine multiple data sets into one on R Studio. I want to explore the data using R functions we learned in class. 
I also want to attempt regression somehow. This is how I loaded the data sets into R using read.csv

```{r}
NFLSeason10 <- read.csv('C:/Users/hmoob/Documents\\pass-2010.csv')
NFLSeason11 <- read.csv('C:/Users/hmoob/Documents\\pass-2011.csv')
NFLSeason12 <- read.csv('C:/Users/hmoob/Documents\\pass-2012.csv')
NFLSeason13 <- read.csv('C:/Users/hmoob/Documents\\pass-2013.csv')
NFLSeason14 <- read.csv('C:/Users/hmoob/Documents\\pass-2014.csv')
NFLSeason15 <- read.csv('C:/Users/hmoob/Documents\\pass-2015.csv')
NFLSeason16 <- read.csv('C:/Users/hmoob/Documents\\pass-2016.csv')
NFLSeason17 <- read.csv('C:/Users/hmoob/Documents\\pass-2017.csv')
NFLSeason18 <- read.csv('C:/Users/hmoob/Documents\\pass-2018.csv')
```
We then combine the data sets
```{r}
NFL_All <- rbind(NFLSeason17, NFLSeason16, NFLSeason15, NFLSeason14, NFLSeason13, NFLSeason12, NFLSeason11, NFLSeason10)
```

Here we use a few functions we did in class to better visualize and understand the data set. Every Year in the NFL there is a few other positions who attempt throws and I did not want their data. 

```{r}
names(NFL_All)
```


Changing string variable to Factor
```{r}
NFLSeason18$Player <- as.factor(NFLSeason18$Player)
```

```{r}
class(NFLSeason18$Player)
```
Ultimately I had to eliminate low outliers so I used subset yo restrict a mininum of 500 yards.

```{r}
NFLData<- subset(NFL_All, NFL_All$Yds > 500)
```

```{r}
boxplot(NFLData$Yds)
```


```{r}
plot(NFLData$Age, NFLData$Yds)
```

```{r}
hist(NFLData$Yds)
```


## Distrubution

## Regression

```{r}
m1 <- lm(Age ~ Yds, data = NFLData)
```
```{r}
summary(m1)
```


```{r}
cor(NFLData$Age, NFLData$Yds)
```


R Markdown is wonderful. It feels like having a stat calculator on hand. The visualization is very helpful.
I had a few problems with Github. But the one that costed me the most was when I tried to delete a file on the website.
It will no longer let me commit or pull/push. 
The help sites helped at time but it was though to trouble shoot as I was not sure with Github program was useful to troubleshoot with. 
In conclusion, I was a little disappointed in not being able to categorize the variable player into what I wanted it to be. 
I was able to look at other cool factors such as age and yards. If, I had more time I would try to see if 
somehow I can combine all the player variables into one, in example 
have Tom Brady as a variable and it would span across all the years.
