---
title: "FinalProject631-02"
author: "Andy Xiong"
date: "5/11/2022"
output: pdf_document
---

We are going to look at multiple NFL Passing Data set from the year 2010-2018. They are all separate data sets so we can look into an individual year. I want to see if we see the trend for passing yards go up over time and see if their were any specific person responsible. I also wanted to try and combine multiple data sets into one on R Studio. I want to explore the data using R functions we learned in class. I also want to attempt regression somehow. This is how I loaded the data sets into R using read.csv

```{r}
NFLSeason10 <- read.csv('C:/Users/hmoob/Documents\\pass-2010.csv')
NFLSeason11 <- read.csv('C:/Users/hmoob/Documents\\pass-2011.csv')
NFLSeason12 <- read.csv('C:/Users/hmoob/Documents\\pass-2012.csv')
NFLSeason13 <- read.csv('C:/Users/hmoob/Documents\\pass-2013.csv')
NFLSeason14 <- read.csv('C:/Users/hmoob/Documents\\pass-2014.csv')
NFLSeason15 <- read.csv('C:/Users/hmoob/Documents\\pass-2015.csv')
NFLSeason16 <- read.csv('C:/Users/hmoob/Documents\\pass-2016.csv')
NFLSeason17 <- read.csv('C:/Users/hmoob/Documents\\pass-2017.csv')
NFLSeason18 <- read.csv('C:/Users/hmoob/Documents\\pass-2018.csv')
```




```{r}
NFL_All <- rbind(NFLSeason17, NFLSeason16, NFLSeason15, NFLSeason14, NFLSeason13, NFLSeason12, NFLSeason11, NFLSeason10)
```

# Topics From Class

## Summarizing Data

```{r}
names(NFL_All)
```


Changing string variable to Factor
```{r}
NFLSeason18$Player <- as.factor(NFLSeason18$Player)
```

```{r}
class(NFLSeason18$Player)
```



```{r}
plot(NFL_All$Age, NFL_All$Yds)
```



## Distrubution

## Regression

```{r}
m1 <- lm(Age ~ Yds, data = NFL_All)
```
```{r}
summary(m1)
```


```{r}
cor(NFL_All$Age, NFL_All$Yds)
```

## R Markdown

## Github


# Conclusion
